### 2022-11-28 README.Rmd
Changes to README.Rmd
Adde d18O proxy to predictor in example. Also changed a line in rgeneric.uneven.AR1.R, so as to prevent 'theta' from being undefined

age = NGRIP_5cm$age
depth = NGRIP_5cm$depth
proxy = NGRIP_5cm$d18O

data = data.frame(age=age,dy=c(NA,diff(age)),depth=depth,depth2=depth^2,proxy=proxy)
formula = dy~-1+depth2

>>>>

age = NGRIP_5cm$age
depth = NGRIP_5cm$depth
d18O = NGRIP_5cm$d18O

data = data.frame(age=age,dy=c(NA,diff(age)),depth=depth,depth2=depth^2,d18O=d18O)
formula = dy~-1+depth2+d18O
